---
title: "R Notebook"
output: html_notebook
---

#Word Embeded Models

This notebook will use word embeded models to explore the corpus of railroad law.Given the relatively small size and narrow focus of the corpus, I am going to test the usefulness of word embeded models on such a corpus.
```{r}
library(text2vec)
library(magrittr)
library(wordVectors)
library(tsne)
library(ggplot2)
library(tibble)
```

```{r}
#prep_word2vec("C:/Users/Joshua/Documents/rdata/railroaddata/railroads_documents","rr_docs.txt",lowercase=T) 

```

```{r}
# rr_model = train_word2vec("rr_docs.txt",output="rr_doc_vectors.bin",threads = 6,vectors = 100,window=12)
```
Since I created the vector space model of railroad law previously, I simply read in this model.This saves an great deal of time as the creation of the model took well over an hour for 397 documents. 
```{r}
rr_model = read.vectors("rr_doc_vectors.bin")
```
###Similarity Searching
The first method of exploration I used was similarity searching.To demonstrate one challenge to using this method, I chose the word "buffalo." As shown below, this returned a list of mostly cities, but I was interested in the animal.Therefore, I need to perform some addition and subtraction on my word vectors.
```{r}
rr_model %>% nearest_to(rr_model[["buffalo"]])
```


Attempting to subtract the cities from the list did not return my desired outcome. 
```{r}
rr_model %>% nearest_to(rr_model[["buffalo"]] - rr_model[[c("ontario","rochester")]])

```
Attempting to add "cattle" removed the cities but did not yield very interesting results. 
```{r}
rr_model %>% nearest_to(rr_model[["buffalo"]] - rr_model[[c("ontario","rochester")]] + rr_model[["cattle"]])
```
Therefore, I looked at the similarity between "buffalo" and "cattle" and found that they are not very similar (.0098 cosine similarity).
```{r}
cosineSimilarity(rr_model[[c("buffalo"),average=F]], rr_model[[c("cattle"), average=F]])

```
I need to use a different approach. Below I used the reject function to attempt to filter out unwanted definitions/meanings/semantics of "buffalo." As the results show, this was also not effective. "Buffalo" the animal is not used enough in the context of an animal in this corpus. 
```{r}
not_that_kind_of_buffalo = rr_model[["buffalo"]] %>%
      reject(rr_model[["city"]]) %>% 
      reject(rr_model[["rochester"]]) %>%   
      reject(rr_model[["ontario"]])%>%   
      reject(rr_model[["utica"]]) 

rr_model %>% nearest_to(not_that_kind_of_buffalo)
```

Now I will take a look at another example.
Looking at the word "sheep" reveals that the animals included in the corpus are types of cargo. 
```{r}
rr_model %>% nearest_to(rr_model[["sheep"]], 20)
```
Interestingly, wool is absent from this above list. Similarly, "sheep" is absent from the similarity search for "wool."

```{r}
rr_model %>% nearest_to(rr_model[["wool"]], 20)
```


Despite the fact that wool and sheep seem unrelated based upon the similarity searching, they do have a fairly high cosine similarity score (0.38). 
```{r}
cosineSimilarity(rr_model[[c("sheep"),average=F]], rr_model[[c("wool"), average=F]])
```
The same is true for hides/cows (0.35).
```{r}
cosineSimilarity(rr_model[[c("cows"),average=F]], rr_model[[c("hides"), average=F]])

```

Thus, the classic king - man + women = queen example should work for sheep and cows. Wool - sheep + cow = hide. 

```{r}
rr_model %>% nearest_to(rr_model[["wool"]] - rr_model[[c("sheep")]] + rr_model[["cow"]], 25)
```

```{r}
rr_model %>% nearest_to(rr_model[["sheep"]] - rr_model[[c("wool")]] + rr_model[["hide"]])
```
```{r}
rr_model[["wool"]] - rr_model[[c("sheep")]] + rr_model[["cow"]]
```

###Plotting Characteristics

Below I experimented with the informaiton gathered in the examples above. One thing that I noticed was that "sheep" was part of a group of animals (but not "buffalo") and that "wool" was part of a commodity. So, I further explored these different types of cargo (living/nonliving) and further divided them as perishable/non perishable. 

```{r}
rr_model %>% nearest_to(rr_model[["eggs"]], 50)

perishable = nearest_to(rr_model, rr_model[[c("eggs", "butter", "vegetables", "asparagus", "cheese", "lettuce", "potatoes", "peas", "margarine", "oranges", "beans", "beef", "lemons", "beeries", "cabbage", "peaches", "peaches", "apples")]], 150)

non_perishable = nearest_to(rr_model, rr_model[[c("cotton", "lumber", "cement", "coal", "iron", "steel", "shingles", "lime", "turpentine", "petroleum", "fertilizer", "salt", "leather")]], 150)

living_cargo = nearest_to(rr_model, rr_model[[c("sheep", "swine", "hogs", "goats", "cattle", "cows", "pigs", "mules", "calves", "poultry")]], 150)

non_living_cargo = nearest_to(rr_model, rr_model[[c("wool", "hides", "meat", "cheese", "grain", "potatoes", "hay", "cotton", "four", "leather", "hops", "fruit", "vegetables", "sugar", "canned", "eggs", "stuffs", "dried", "groceries", "canned")]], 150)
                     
lifelike = model[[names(living_cargo), average =F]]
lifeless = model[[names(non_living_cargo), average =F]]

cargo_words = c("eggs", "butter", "vegetables", "asparagus", "cheese", "lettuce", "potatoes", "peas", "margarine", "oranges", "beans", "beef", "lemons", "beeries", "cabbage", "peaches", "peaches", "apples", "cotton", "lumber", "cement", "coal", "iron", "steel", "shingles", "lime", "turpentine", "petroleum", "fertilizer", "salt", "leather", "wool", "hides", "meat", "cheese", "grain", "potatoes", "hay", "cotton", "four", "leather", "hops", "fruit", "vegetables", "sugar", "canned", "eggs", "stuffs", "dried", "groceries", "canned", "sheep", "swine", "hogs", "goats", "cattle", "cows", "pigs", "mules", "calves", "poultry")

cargo = rr_model[rownames(rr_model) %in% cargo_words, ]

perishable_score = cargo %>% cosineSimilarity(rr_model[[c("eggs", "butter", "vegetables", "asparagus", "cheese", "lettuce", "potatoes", "peas", "margarine", "oranges", "beans", "beef", "lemons", "beeries", "cabbage", "peaches", "peaches", "apples")]])

non_perishable_score = cargo %>% cosineSimilarity(rr_model[[c("cotton", "lumber", "cement", "coal", "iron", "steel", "shingles", "lime", "turpentine", "petroleum", "fertilizer", "salt", "leather")]])

non_living_score = cargo %>% cosineSimilarity(rr_model[[c("wool", "hides", "meat", "cheese", "grain", "potatoes", "hay", "cotton", "four", "leather", "hops", "fruit", "vegetables", "sugar", "canned", "eggs", "stuffs", "dried", "groceries", "canned")]])
                                              
living_score = cargo %>% cosineSimilarity(rr_model[[c("sheep", "swine", "hogs", "goats", "cattle", "cows", "pigs", "mules", "calves", "poultry")]]) 

dfpvnp <- data_frame(x = perishable_score[, 1], y = non_perishable_score[, 1], labels = rownames(cargo))

dflvnl <- data_frame(x = living_score[, 1], y = non_living_score[, 1], labels = rownames(cargo))


#plot(perishable_score,non_perishable_score,type='n',main="Top 300 cargo words plotted by their similarity to perishable\n(x axis) and non perishable (y axis).")
#text(perishable_score,non_perishable_score,labels=rownames(cargo),cex=.7) 
#abline(a=0,b=1)

#some_fish = nearest_to(model,model[[c("fish","salmon","trout","shad","flounder","carp","roe","eels")]],150)
#fishy = model[[names(some_fish),average=F]]
```
Below is a plot of perishable(ness).
```{r}
ggplot (dfpvnp, aes(x, y, label = labels)) + geom_text() + geom_point() + coord_equal() + xlab("Perishable Score") + ylab("Non Perishable Score") + ggtitle("Perishable(ness)") + geom_abline(intercept = 0, slope = 1)

```

Living vs Non living
```{r}
ggplot (dflvnl, aes(x, y, label = labels)) + geom_text() + geom_point() + coord_equal() + xlab("Living Score") + ylab("Not Living Score") + ggtitle("Alive(ness)") 
```


#Clustering

Simply plotting the model shows some interesting clusters. For example, the words "negligence, "injury," "damage," "jury," and "defendent" are all clustered together.
```{r}
plot(rr_model)
```
Similarity searching confirms the existence of this cluster.
```{r}
rr_model %>% nearest_to(rr_model[["injury"]])
```



```{r}
chronam_vectors = read.vectors(pipe("gunzip -c ~/Dropbox/rmp2vec/shorter_chronam.txt.gz"),nrow=50000,vectors = 500)
```

